%! Author = jason
%! Date = 12/04/20

% Preamble
\documentclass[11pt]{article}

\title{Curriculum Vitae}
\author{Jason Pickens}

% Packages
\usepackage{fontawesome}
\usepackage{hyperref}

% Document
\begin{document}

    \maketitle
    \pagenumbering{gobble}


    \section{Contact Details}
    \label{sec:contact-details}

    \subsection{Mobile}
    \label{subsec:mobile}
    \faMobile \href{tel:+64-21-118-84533}{+64-21-118-84533}

    \subsection{Email}
    \label{subsec:email}
    \faEnvelopeO \href{mailto:jason.pickensnz@gmail.com}{jason.pickensnz@gmail.com}

    \subsection{GitHub}
    \label{subsec:github}
    \faGithub \href{https://github.com/steinybot}{https://github.com/steinybot}
    \faGithub \href{https://github.com/bottech}{https://github.com/bottech}

    \subsection{LinkedIn}
    \label{subsec:linkedin}
    \faLinkedin \href{https://www.linkedin.com/in/jason-pickens}{https://www.linkedin.com/in/jason-pickens}


    \section{Career Highlights}
    \label{sec:career-highlights}
    Working with my heroes at Lightbend.
    Leading Geneious Prime team.
    Implementing reactive microservices.
    Championing reactive design.
    Introducing Scala and functional programming.
    Integrating healthcare systems.
    Supporting enterprise customers.


    \section{Experience}
    \label{sec:experience}

    \subsection{Senior Engineer}
    \label{subsec:senior-engineer}
    \href{https://www.lightbend.com/}{Lightbend}
    September 2019

    I joined Lightbend to work on version 2 of
    \href{https://developer.lightbend.com/docs/console/current/}{Lightbend Console}
    which in an observability tool for gathering insights into Akka Cluster, Play and Lagom
    applications running on Kubernetes (k8s).

    My primary responsibilities were to create new backend services using Akka-gRPC and Akka-HTTP
    and to build the manifests for the k8s resources, including Prometheus, Grafana and ELK .
    I also maintained the CICD pipelines and infrastructure.

    \subsection{Development Team Lead}
    \label{subsec:development-team-lead}
    \href{https://www.geneious.com/about/}{Biomatters}
    January 2019 -- September 2019

    I lead a team of six to develop \href{https://www.geneious.com/prime/}{Geneious Prime},
    a molecular biology and sequence analysis application.

    I worked closely with the project owner to define the road map and then with the team to plan
    scope and deliver the work.
    I provided technical leadership while also modernising the development processes.

    \subsection{Full Stack Developer}
    \label{subsec:full-stack-developer}
    \href{https://www.geneious.com/about/}{Biomatters}
    June 2017 -- January 2019

    I initially joined Biomatters as a key member of the cloud team to create a new bioinformatics
    platform powering \href{https://www.geneious.com/biopharma/}{Geneious Biologics}.

    My role was to bring my Scala experience to revamp the platform and upskill the rest of the
    team.
    I led several design decisions including the creation of new microservices written with Lagom
    and leveraging patterns such as CQRS and Event Sourcing as well as technologies like Apache
    Spark and AWS Batch/Lambda.

    \subsection{Software Engineer}
    \label{subsec:software-engineer}
    \href{https://orionhealth.com/nz/}{Orion Health}
    January 2010 -- June 2017

    My first job as a graduate was at Orion Health working on
    \href{https://www.lyniate.com/rhapsody/}{Rhapsody}, an integration engine, and then named
    Symphonia, a messaging toolkit.

    Over the years I designed and implemented several new features.
    I was primarily responsible for supporting and maintaining Symphonia support which lead me to
    do several rotations in the Rhapsody development support team.

    I prototyped the very first Rhapsody-as-a-service initiative from which we formed a new team
    to work on a new cloud native application.
    It was here where I first used Scala commercially and introduced it into the project.


    \section{Skills}
    \label{sec:skills}
    Scala, Java
    Akka, Akka-Streams, Akka-HTTP, Play, Lagom
    Kubernetes, Jsonnet, Docker
    Mesos, DC/OS, Kafka, Spark, Prometheus, Grafana, ELK
    AWS, GKE
    Vagrant, Puppet, Terraform
    Git
    gRPC, REST, GraphQL
    React, Angular, UIKit, Scala.js, Slinky, Sangria


    \section{Education}
    \label{sec:education}

    \subsection{BSc Computer Science}
    \label{subsec:bsc-computer-science}
    University of Auckland
    2006--2009

    Throughout my conjoint degrees I maintained a GPA of over 7.5.

    I majored in Computer Science and took papers such as Algorithms and Data Structures, Applied
    Algorithmics, Human Computer Interaction, Artificial Intelligence, and Computer Graphics.

    \subsection{BCom Information System}
    \label{subsec:bcom-information-system}
    University of Auckland
    2006--2009

    The coursework covered all aspects of the SDLC with a focus on relational databases and ended in
    a year-long project for an external business.


    \section{References}
    \label{sec:references}
    Available upon request.


    \section{About Me}
    \label{sec:about-me}
    Born and raised in New Zealand.
    Married with a young daughter.

    \subsection{Hobbies}
    \label{subsec:hobbies}
    Spearfishing, Snowboarding, Craft Beer, Gaming, and Board Games.

    \subsection{Podcasts}
    \label{subsec:podcasts}
    Scala Love, CoRecursive, Functional Geekery, Risky Business, Lightbend, Y Combinator,AWS
    TechChat and The New Stack.

\end{document}